\textbf{Computational Fuzzy Extractors}

### 2013-06-23 CompFuzzExt.tex
Cleaning up notes in Section B

\title{\textbf{Computational Fuzzy Extractors}}
%\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
% \and Xianrui Meng \and Leonid Reyzin}
\author{}
\begin{document}
\maketitle

@@

The following theorem states the main technical result of this section, which is of potential interest outside our specific setting. The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$ (but for $n$ and $m$ reduced by the amount of fixed symbols).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter, $\alpha$ be polynomial in $n$, and $\beta=\beta(n)=\omega(1)$. \lnote{rephrase so that $q=q(n)$ and$q^{-\beta}$ is negl in $n$}
Let $U$ denote the uniform distribution over $Z^m$ for an alphabet $Z\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |Z|)$ symbol fixing source over $Z^{m+\alpha}$.
If $\distLWE_{n, m,q, U}$ is secure, then $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ is also secure.
\end{theorem}

\thref{thm:blockLWE} also holds for an arbitrary error distribution~(not just uniform error) in the following sense.  Let $\chi$ be an arbitrary error distribution.  Define $\chi'$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.  Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.

The intuition for this result is as follows.  Providing a single sample with no error ``fixes'' at most a single variable.  Thus, if there are significantly more variables than samples with no error,  search $\LWE$ should still be hard.  We are able to show a stronger result that $\distLWE$ is still hard.  The nontrivial part of the reduction is using the additional $\alpha+ \beta$ variables  to ``explain'' a random value for the last $\alpha$ samples, without knowing the other variables.  The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.  A formal proof is in \secref{sec:proof of block theorem}.

@@

\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE}.  Efficiency follows by \lemref{lem:i t poly time}.  For a more detailed explanation of parameters see \secref{ssec:block params}. \lnote{to satsify \thref{thm:blockLWE} condition on $\beta$ is easy here, because $q$ is at least $n^2$, so superconstant $\beta$ is enough}
\end{proof}

@@

%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
\begin{proof}
We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$ \lnote{are we using $W$ or $\chi$ notation?}.  If the blocks are fixed to some other value, the reduction is essentially the same\lnote{isn't the point of a block fixing source that we don't know which values are fixed and to what? At least in the extractor literature, that would seem to be crucial---else, extraction is trivial}.  For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.  For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.  Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.  We use similar notation for the complement of $T$, denoted $T^c$.

@@

Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.
Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ with advantage $\epsilon>1/\poly(n)$m
where $\chi'_i = \chi_i$ for $i\leq m$ \lnote{what's $\chi_i$?} and $\chi_i \overset{d}= 0$ otherwise. \lnote{we should probably swap $\chi$ and $\chi'$ to be consistent about the use of primes} Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ . Then
\[
|\Pr[D(\vA, \vA X+\chi') = 1] - \Pr[D(\vA, U =1]|> \epsilon.
\]
We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.  Let $\vA'$ denote the uniform distribution over $\Fq^{m\times n}$, $X'$ denote the uniform distribution over $\Fq^n$, and $U'$ denote the uniform distribution over $\Fq^{m}$ .  We will build a distinguisher $D'$ of polynomial size for which
\begin{align}
\label{eq:block LWE dist}
|\Pr[D'(\vA', \vA'X'+\chi) = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
\end{align}
$D'$  will make a single call to $D$, so we focus on how to prepare a random block-fixing instance for $D$ from the random instance that $D'$ is given.  The code for $D'$ is given in \figref{fig:perfectLWEreduction}.

%\begin{figure}[p]
%\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
\item Choose $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$ uniformly at random. Initialize $\vQ \in \Fq^{m\times (\alpha+\beta)}$  to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, for uniformly chosen $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Choose $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ uniformly at random.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.\label{step:find columns}
\item For all $j\notin T$, $1\le j \le \alpha+\beta$:\lnote{swapped $i$, $j$ and shifted}\label{step:fill in matrix}
\subitem Choose $x_{n+j}\overset{\$}\leftarrow \Fq$ uniformly at random.  
\subitem For $i=1,..., m$:
\subsubitem Choose $\vQ_{i,j}\overset{\$}\leftarrow \Fq$ uniformly at random.
\subsubitem Set $b_i^* = b_i^* + \vQ_{i,j} x_{n+j}$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Choose a row vector $\gamma_i \leftarrow \Fq^{1 \times \alpha}$ uniformly at random.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+\alpha})^{\mathsf{T}}$
\item For $i=m+1,\dots, m+\alpha$:
\subitem Set $\va_i \leftarrow \va^*_i$
\subitem Set $b_i = b_i^*$.
\item Output $D(\vA, \vb)$. 
\end{enumerate}
%\end{framed}
%\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
%\label{fig:perfectLWEreduction}
%\end{figure}
The distinguisher $D'$ has an advantage when $\vS$ is of rank $\alpha$.  This occurs with overwhelming probability:
\begin{claim}
\label{cl:full rank matrix 5.2}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
Direct result of \clref{cl:full rank matrix} when $\beta = \omega(1)$ in $n$. \lnote{rephrase to say that it follows from the assumption that $q^{-\beta}$ is negligible.}
\end{proof}
\begin{corollary}
$
|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}
\lnote{why is this a corollary?  A corollary should follow from something above it, usually}

We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $D'$ prepares a good instance for $D$ in this case. We show this in the following three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix subject to the condition that $\rank(\vS) = \alpha$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
\item If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then the conditional distribution $\vb\,|\,\vA$ is also uniform.
\end{enumerate}

@@

Thus, we restrict attention to the $m\times \alpha$ submatrix of $\vA$ that corresponds to $\vQ_T$ in $\vA^*$ (note that these values are $0$ in $\vA^*$).  Consider a particular row $i$. That row is computed as $\gamma_i \vS_{T}$.  Since $\vS_T$ is a full rank square matrix and $\gamma_i$ is uniformly and independently generated, that row is also uniform and independent of other entries in $\vA$.
% In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.  Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.  Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.  Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5. For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number. Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors. Therefore, the entire matrix $\vA$ is a truly random matrix.  This completes the claim.
\begin{claim}
\label{cl:random ax+e}
If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$, where
\item $e_i = e_i'$ for $1\leq i\leq m$,
\item $e_i = 0$ for $m<i\leq m+\alpha$,
\item $x_i = x_i'$ for $1\leq i \leq n$,
\item and $x_i$ is uniform and independent of $\vA$ and $\ve'$ for $n<i\le n+\alpha+\beta$,
Partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.  Define the remaining variables $\vx_T$ as the solution to the following system of equations.
\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  
A solution $\vx_T$ exists as $\vS_T$ is full rank. Moreover, it is uniform and independent of $\vA$ and $\ve'$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve'$. Note that $\vb^*=\vA^*\vx+\ve$ before step~\ref{step:randomization} \lnote{this requires careful attention to the algorithm and the definition of $\vx$, not much different from the steps below. Why do the steps below get the attention and this one doesn't? Perhaps for the above stuff say "by inspection, particularly Step 6, and for below part say "by inspection, we show it formally below"}.
Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.  The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
We have the following for $1\leq i\leq m$:
\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
Recall that $b_i =b_i^* + \gamma_i(b_{m+1}^*,..., b_{m+k}^*)$.  We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
\\&=  \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
This completes the proof of the claim.
\begin{claim}\label{clm:random b}
If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then $\vb\,|\,\vA$ is also uniform.
Since $\vR, \vS$, and $\vQ$ are chosen independently of $\vb'$, the distribution $\vb'\,|\,\vA^*$ is uniform.
Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}. Its first $m$ coordinates are  computed by adding the uniform vector $\vb'$ to values that are independent of $\vb^*$, and its remaining $\alpha$ coordinates $b^*_{m+1},\dots,b^*_{m+\alpha}$ are   chosen uniformly.  Thus $\vb^*\,|\,\vA^*$ is uniform.

\lnote{I would delete this paragraph and the next one, and replace with the one below} We will now show that $\vb\,|\,(\vA, \vA^*)$ is uniformly distributed, therefore, showing that $\vb\,|\,\vA$ is uniform.  Indeed, let $\vgamma$ represent the matrix formed by $\gamma_{i}$.

 The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$ \lnote{why?  And does it depend on the choice of the set $T$ in step 5 being deterministic? and do you need this? Can't you just write $\vb\,|\,\vA=\vb\,|\,(\vA^*,\Gamma)$, because $\vA$ is a function of $\vA^*, \Gamma$?}.  Thus, $\vb\,|\,(\vA, \vA^*)$ has the same distribution as $\vb\, |\,(\vA, \vA^*, \vgamma)$.  The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$\lnote{not sure what the previous sentence means}.  Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$. Recall that 
 \[
 \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
\]
Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.

\lnote{I got confused by the two paragraphs above --- see comments --- so I wrote it differently.  If you agree, delete the two paragraphs above.}

>>>>

\title{\textbf{Computational Fuzzy Extractors}}
\author{Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.  The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
%\author{}
\begin{document}
\maketitle

@@

The following theorem states the main technical result of this section, which is of potential interest outside our specific setting. The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$ (but for $n$ and $m$ reduced by the amount of fixed symbols).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter, $m, \alpha$ be polynomial in $n$, and $q=\poly(n)$ be a prime and $\beta\in\mathbb{Z^+}$ be such that $q^{-\beta} = \ngl(n)$. 
Let $U$ denote the uniform distribution over $Z^m$ for an alphabet $Z\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |Z|)$ symbol fixing source over $Z^{m+\alpha}$.
If $\distLWE_{n, m,q, U}$ is secure, then $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ is also secure.
\end{theorem}

\thref{thm:blockLWE} also holds for an arbitrary error distribution~(not just uniform error) in the following sense.  Let $\chi'$ be an arbitrary error distribution.  Define $\chi$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.  Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.  We show this stronger version of the theorem in \apref{sec:proof of block theorem}.

The intuition for this result is as follows.  Providing a single sample with no error ``fixes'' at most a single variable.  Thus, if there are significantly more variables than samples with no error,  search $\LWE$ should still be hard.  We are able to show a stronger result that $\distLWE$ is still hard.  The nontrivial part of the reduction is using the additional $\alpha+ \beta$ variables  to ``explain'' a random value for the last $\alpha$ samples, without knowing the other variables.  The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.

@@

\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE} .  Since \lemref{lem:uniform LWE decision} requires that $q = O(n^{3/2})$, setting  $\beta = \omega(1)$ is sufficient for $q^{-\beta} = \ngl(n)$ as required in \thref{thm:blockLWE}.  Efficiency follows by \lemref{lem:i t poly time}.  For a more detailed explanation of parameters see \secref{ssec:block params}. 
\end{proof}

@@

%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
\begin{proof}
We assume that all of the fixed blocks are located at the end and their fixed value is $0$.  If the blocks are fixed to some other value, the reduction is essentially the same
 In the reduction, the distinguisher is allowed to depend on the source and can know the positions of the fixed blocks and their values.  For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.  For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.  Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.  We use similar notation for the complement of $T$, denoted $T^c$.  For a matrix or vector we use $\mathsf{T}$ to denote the transpose.  We use $i$ as a index into matrix rows and the error vector and $j$ as an  index into columns and the solution vector.

@@

Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta$ be such that $q^{-\beta} = \ngl(n)$.  All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.  Let $\chi'$ be some error distribution over $\Fq^m$ and let $\chi$ over $\Fq^{m+n}$ be defined by sampling $\chi'$ to obtain values on dimensions $1,..., m$ and then appending $\alpha$ 0s.

Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi}$ with advantage $\epsilon>1/\poly(n)$.
Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ . Then
\[
|\Pr[D(\vA, \vA X+\chi) = 1] - \Pr[D(\vA, U )=1]|> \epsilon.
\]

We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.  Let $\vA'$ denote the uniform distribution over $\Fq^{m\times n}$, $X'$ denote the uniform distribution over $\Fq^n$, and $U'$ denote the uniform distribution over $\Fq^{m}$ .  We will build a distinguisher $D'$ of polynomial size for which
\begin{align}
\label{eq:block LWE dist}
|\Pr[D'(\vA', \vA'X'+\chi') = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
\end{align}
$D'$  will make a single call to $D$, so we focus on how to prepare a random block-fixing instance for $D$ from the random instance that $D'$ is given.  The code for $D'$ is given in \figref{fig:perfectLWEreduction}.

\begin{figure}[p]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi'$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
\item Choose $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$ uniformly at random. Initialize $\vQ \in \Fq^{m\times (\alpha+\beta)}$  to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, for uniformly chosen $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Choose $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ uniformly at random.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.\label{step:find columns}
\item For all $1\le j \le \alpha+\beta$, $j\notin T$:
\label{step:fill in matrix}
\subitem Choose $x_{n+j}\overset{\$}\leftarrow \Fq$ uniformly at random.  
\subitem For $i=1,..., m$:
\subsubitem Choose $\vQ_{i,j}\overset{\$}\leftarrow \Fq$ uniformly at random.
\subsubitem Set $b_i^* = b_i^* + \vQ_{i,j} x_{n+j}$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Choose a row vector $\gamma_i \leftarrow \Fq^{1 \times \alpha}$ uniformly at random.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+\alpha})^{\mathsf{T}}$
\item For $i=m+1,\dots, m+\alpha$:
\subitem Set $\va_i \leftarrow \va^*_i$
\subitem Set $b_i = b_i^*$.
\item Output $D(\vA, \vb)$. 
\end{enumerate}
\end{framed}
\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}

The distinguisher $D'$ has an advantage when $\vS$ is of rank $\alpha$.  This occurs with overwhelming probability:
\begin{claim}
\label{cl:full rank matrix 5.2}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
Direct result of \clref{cl:full rank matrix} because $q^{-\beta} = \ngl(n)$.
\end{proof}
The probability that a random $\vS$ is not full rank is $\ngl(n)$ so the distinguisher $D$ must still have an advantage when the matrix $\vS$ is full rank.  That is,
\[
|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
\]

It suffices to show that $D'$ prepares a good instance for $D$ conditioned on $\vS$ being full rank. We show this in the following three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix subject to the condition that $\rank(\vS) = \alpha$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
\item If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then the conditional distribution $\vb\,|\,\vA$ is also uniform.
\end{enumerate}

@@

Thus, we restrict attention to the $m\times \alpha$ submatrix of $\vA$ that corresponds to $\vQ_T$ in $\vA^*$ (note that these values are $0$ in $\vA^*$).  Consider a particular row $i$. That row is computed as $\gamma_i \vS_{T}$.  Since $\vS_T$ is a full rank square matrix and $\gamma_i$ is uniformly and independently generated, that row is also uniform and independent of other entries in $\vA$.
% In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.  Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.  Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.  Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5. For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number. Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors. Therefore, the entire matrix $\vA$ is a truly random matrix.  This completes the claim.
\end{proof}
\begin{claim}
\label{cl:random ax+e}
If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$, where
\begin{itemize}
\item $e_i = e_i'$ for $1\leq i\leq m$,
\item $e_i = 0$ for $m<i\leq m+\alpha$,
\item $x_j = x_j'$ for $1\leq j \leq n$,
\item and $x_j$ is uniform and independent of $\vA$ and $\ve'$ for $n<j\le n+\alpha+\beta$,
\end{itemize}
\end{claim}
\begin{proof}
Partially define $\vx$ as $x_j = x_j'$ if $1\leq j \leq n$ and $x_j$ as the value generated in step~\ref{step:fill in matrix} for $j>n $ and $j\not\in T$.  Define the remaining variables $\vx_T$ as the solution to the following system of equations.
\begin{eqnarray}
\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  \label{eq:x t solution}
\end{eqnarray}
A solution $\vx_T$ exists as $\vS_T$ is full rank. Moreover, it is uniform and independent of $\vA$ and $\ve$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve$.

We now show that $\vb^* = \vA^* \vx+\ve$.  All entries in matrix $\vQ$ corresponding to variables in $T$ are set to zero.  Thus, the values of $\vx^T$ do not affect $b_i$ for $1\le i \le m$.  The values of $\vx_{T^c}$ are manually set, and $\vQ_{i, j} \vx_{j}$ is added to the corresponding $\vb_i$.  Thus, for $1 \leq i \le m$, we have $\vb^* = \vA^*\vx+\ve$.   For $m< i$, this constraint is also satisfied by the values of $\vx_T$ set in Equation~\ref{eq:x t solution}.

Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.  The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
Recall the other rows are not modified.  We have the following for $1\leq i\leq m$:
\begin{align*}
\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
\end{align*}
Recall that $b_i =b_i^* + \gamma_i(b_{m+1}^*,..., b_{m+k}^*)$.  We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
\begin{align*}
(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
\\&=  \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
\end{align*}
This completes the proof of the claim.
\end{proof}
\begin{claim}\label{clm:random b}
If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then $\vb\,|\,\vA$ is also uniform.
\end{claim}
\begin{proof}
Since $\vR, \vS$, and $\vQ$ are chosen independently of $\vb'$, the distribution $\vb'\,|\,\vA^*$ is uniform.
Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}. Its first $m$ coordinates are  computed by adding the uniform vector $\vb'$ to values that are independent of $\vb^*$, and its remaining $\alpha$ coordinates $b^*_{m+1},\dots,b^*_{m+\alpha}$ are   chosen uniformly.  Thus $\vb^*\,|\,\vA^*$ is uniform.
